
\documentclass{article}
\usepackage{amsmath}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\title{Problem Formulation: Optimization of Energy Efficiency and Execution Time in Cloud Computing}
\author{Tom Jardin}
\date{\today}

\begin{document}

\maketitle

\section*{Introduction}
This document outlines the problem formulation for optimizing energy efficiency and execution time in a cloud computing environment using various optimization techniques. The objective is to develop models that minimize energy consumption and execution time by applying Mixed Integer Linear Programming (MILP), Simulated Annealing (SA), Genetic Algorithms (GA), and Multi-Objective Goal Programming (MOGP).

\section*{Problem Statement}
\textbf{Objective:} To minimize energy consumption and execution time in a cloud computing environment.

\textbf{Key Features:}
\begin{itemize}
    \item CPU usage
    \item Memory usage
    \item Network traffic
    \item Power consumption
    \item Number of executed instructions
    \item Execution time
    \item Task type, priority, and status
\end{itemize}

\section*{Mixed Integer Linear Programming (MILP) Formulation}
\textbf{Objective:} Minimize the total cost of energy consumption and execution time.

\begin{align*}
    \text{Minimize } Z &= \alpha \times \text{Energy Consumption} + \beta \times \text{Execution Time}
\end{align*}

\textbf{Subject to:}
\begin{align*}
    &\text{Resource Constraints: } \sum_{i} r_{ij} \times x_{it} \leq R_{j}^{\text{max}}, \quad \forall j, t \\
    &\text{Task Completion Constraints: } \sum_{t} x_{it} = 1, \quad \forall i \\
    &\text{Binary Constraints on decision variables.}
\end{align*}

\section*{Simulated Annealing (SA) Approach}
\textbf{Objective:} Iteratively minimize energy consumption and execution time by exploring different configurations.

\textbf{Steps:}
\begin{enumerate}
    \item Start with an initial solution \(S\) and initial temperature \(T\).
    \item For each iteration, generate a new solution \(S'\) in the neighborhood of \(S\).
    \item Compute the change in cost \(\Delta E = E(S') - E(S)\).
    \item If \(\Delta E < 0\), accept \(S'\). Else, accept \(S'\) with probability \(\exp(-\Delta E / T)\).
    \item Decrease the temperature \(T\) and repeat until convergence.
\end{enumerate}

\section*{Genetic Algorithms (GA) Approach}
\textbf{Objective:} Evolve task allocation strategies to minimize energy consumption and optimize execution time.

\textbf{Steps:}
\begin{enumerate}
    \item Initialize a population of chromosomes (task allocations).
    \item Evaluate fitness: \(f(\text{chromosome}) = w_1 \times \text{Energy Consumption} + w_2 \times \text{Execution Time}\).
    \item Selection: Choose the fittest chromosomes.
    \item Crossover: Create offspring by combining pairs of chromosomes.
    \item Mutation: Introduce small changes to chromosomes.
    \item Repeat until convergence or maximum iterations.
\end{enumerate}

\section*{Multi-Objective Goal Programming (MOGP) Formulation}
\textbf{Objective:} Balance multiple goals like minimizing energy consumption and execution time.

\textbf{Formulation:}
\begin{enumerate}
    \item Define Goals: \(G_1\) - Minimize Energy, \(G_2\) - Minimize Execution Time.
    \item Formulate deviation variables (\(d^+\) and \(d^-\)) for each goal.
    \item Minimize the weighted sum of deviations: \(\text{Minimize } Z = w_1 \times d_1^+ + w_2 \times d_2^-\).
    \item Subject to: Goal constraints, resource constraints.
\end{enumerate}

\end{document}
